---
title: "M55 - Query & Report"
output: 
  flexdashboard::flex_dashboard:
    source_code: embed 
runtime: shiny
---

```{r global, include=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(DT)
library(tidyr)
library(data.table)
library(rmarkdown)
library(stringr)
dataset <- read_excel("input_data/retail.xlsx") 
dataset <- dataset %>% 
  select(`Order ID`, `Order Date`, Category, `Sub-Category`,
         `Product Name`, Quantity, Profit)
dataset$`Order Date` <- as.Date(dataset$`Order Date`)
```

Main  
=======================================================================

### 

```{r}
# `shinyApp` needs two arguments: `ui` and `server`.    
# `ui` is an object for "User Interface".  
# `ui` includes input panels and other design features.  
# `server` uses `input` to generate `output`  

# Part 1. create `ui`  
ui <- fillPage(
  fillCol(flex = c(NA, 1), 
    inputPanel(
      # selectInput("region", "Region:", choices = colnames(WorldPhones)),
      dateRangeInput(inputId = "dt_rng", label = "Date Range",
                     min = min(dataset$`Order Date`), start = max(dataset$`Order Date`)-14,
                     max = max(dataset$`Order Date`), end = max(dataset$`Order Date`)),
      radioButtons(inputId = "class", label = "Category",
                   choices = c("Furniture", "Office Supplies", "Technology")),
      downloadButton("downloadData", label = "Save to CSV"),
      actionButton("render_docx", "Report using csv")
    ),
    DT::dataTableOutput("dataset")
  )
)
# Part 2. create `server`   
server <- function(input, output) {  
  # Data Filtering using input values  
  datasetFiltered <- reactive({
    dataset %>%
      filter(`Order Date` >= input$dt_rng[1] & `Order Date` <= input$dt_rng[2]) %>%
      filter(Category == input$class)
  })
  # Display the filtered table  
  output$dataset <- DT::renderDataTable({
    datasetFiltered()
  })
  # Download filtered table to .csv  
  # output$downloadData <- downloadHandler(
  #   filename = function() {
  #     "dataset_filtered.csv"
  #   },
  #   content = function(file) {
  #     write.csv(datasetFiltered(), file)
  #   }
  # )
  # Use the saved .csv to render a docx
  # observeEvent(input$render_docx, {
  #   # library(beepr); beep() # simple way to check if this block is responding  
  #   rmarkdown::render(
  #     input = "M55-summary_docx.Rmd",
  #     output_file =
  #       paste0("summary_report_",
  #              Sys.time() %>%
  #                strptime("%Y-%m-%d %H:%M:%OS") %>%
  #                str_replace_all(":", "-") %>%
  #                str_replace_all(" ", "-"),
  #              ".docx"),
  #     encoding = "UTF-8")
  # })
}

# Part 3. use `shinyApp()` to combine `ui` and `server`    
shinyApp(ui, server, options = list(height = 600))
```  

References  
=====================================  

1. `flexdashboard`에서 `shiny`를 사용하는 법     
    + <https://rmarkdown.rstudio.com/flexdashboard/shiny.html>
    + 예제 
        + <https://beta.rstudioconnect.com/jjallaire/shiny-embedding> 
        + `jjallaire`는 Rstudio의 CEO입니다!    

<br>  

2. `shiny`에서 `DataTables`을 사용하는 법     
    + `M12` appendix 참조  
    + <https://shiny.rstudio.com/articles/datatables.html>  

<br>  

3. ~~`DataTables`에서 객체를 `csv`로 저장하는 법~~  
    + 아래 링크에서 "2. Buttons" 
    + <https://rstudio.github.io/DT/extensions.html>  
    + `shiny`환경에서는 잘 안되기 때문에 `shiny`의 `downloadHandler()`를 이용하자.  

<br>  

4. `shiny`의 `downloadHandler()` 사용하는 법   
    + <https://shiny.rstudio.com/reference/shiny/0.14/downloadHandler.html>  
    + 예제: <https://shiny.rstudio.com/gallery/download-file.html>   
    + ~~Rstudio 나랑 장난하니?~~    
        + "Note that the download button does not work well in the RStudio viewer."  
        + "Open in Browser"를 눌러주세요.  
        + <https://stackoverflow.com/questions/25984138/shiny-app-downloadhandler-does-not-produce-a-file>

<br>  

5. `actionButton`을 이용한 docx 렌더링  
    + <https://shiny.rstudio.com/articles/action-buttons.html>  
    + 바탕화면 폴더 이름 인식하기
        + <https://stackoverflow.com/questions/25886987/find-the-desktop-path-in-r>  
    + `M28` 참조  

