---
title: "rmd pdf template "  
author: "Learning Spoons"  
date: "`r Sys.Date()`"  
output:   
  pdf_document:  
    latex_engine: xelatex  
    highlight: haddock  
    keep_tex: true  
    pandoc_args: [
     "-V", "classoption=twocolumn"
    ]
    includes:    
      in_header: rmd-pdf-template_files/latex-topmatter.tex  
  smaller: true
mainfont: NanumGothic
classoption: a4paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown 한글 

Code의 9,10,11 번째 라인의 pound sign(#)을 제거하고 위의 줄과 indent를 맞추면 2 컬럼의 문서가 render 됩니다.  
<http://rmarkdown.rstudio.com>.   
When you click the **Knit** button a document will be generated.  

```{r cars}
summary(cars)
```

## Including Plots

```{r pressure, echo=FALSE, fig.height = 3}
plot(pressure)
```

## Line Numbering  

```{#numCode .R .numberLines}
x <- 1:10
y <- x^2
plot(x,y)
"Hello"
```

```{r, echo=FALSE}
x <- 1:10
y <- x^2
y/x 
"Hello"
```

## R Markdown 한글 

Code의 9,10,11 번째 라인의 pound sign(#)을 제거하고 위의 줄과 indent를 맞추면 2 컬럼의 문서가 render 됩니다.  
<http://rmarkdown.rstudio.com>.   
When you click the **Knit** button a document will be generated.  

```{r}
summary(cars)
```


## R Markdown 한글 

Code의 9,10,11 번째 라인의 pound sign(#)을 제거하고 위의 줄과 indent를 맞추면 2 컬럼의 문서가 render 됩니다.  
<http://rmarkdown.rstudio.com>.   
When you click the **Knit** button a document will be generated.  

```{r}
summary(cars)
```


 
