---
title: "tidyr "
author: "LearningSpoonsR "
date: "`r Sys.Date()`"
fontsize: 9pt
output:
  beamer_presentation:
    theme: "CambridgeUS"
    colortheme: "rose"
    latex_engine: xelatex
    # keep_tex: true
    # template: myTemplate.tex
    includes:
      in_header: myRmdBeamerStyle/latex-topmatter.tex
classoption: t
mainfont: NanumGothic
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(background = '718CBA')
```

## beamer@RMarkdown

- RMarkdown  
- pdf 조판을 위한 texlive 엔진  
- slide형태의 pdf를 만드는 beamer 패키지 (R 패키지가 아니라 tex 패키지)  
- 한글 및 twocolumn layout을 위한 `latex-topmatter.tex` (베포해드리는 `rmd-beamer.Rmd` 템플릿의 하위 폴더에 있습니다.)

## 0. Let's start!

\begcols
\begcol{.48\textwidth}

```{r, message=FALSE}
source("infile-tidyr.R")
library(tidyverse) # Wickham's
library(sqldf)
```

- Part I. Join  
- Part II. Tidy data  

\endcol
\begcol{.48\textwidth}


\endcol
\endcols


## Part I. Join  

\begcols
\begcol{.48\textwidth}

```{r}
df1
df2
```

\endcol
\begcol{.48\textwidth}

- 4 types of join

\endcol
\endcols

## I-1. Inner Join  

```{r, eval=FALSE}
inner_join(df1, df2)
merge(x = df1, y = df2, by = "CustomerId")
sqldf("SELECT CustomerId, Product, State 
       FROM df1 JOIN df2 USING(CustomerID)")   
```

```{r, echo=FALSE}
inner_join(df1, df2)
```

## I-2. Left Join 

```{r, eval=FALSE}
left_join(df1, df2)
merge(x = df1, y = df2, by = "CustomerId", all.x = TRUE)
sqldf("SELECT CustomerId, Product, State 
       FROM df1 LEFT JOIN df2 USING(CustomerID)")  
```

```{r, echo=FALSE}
left_join(df1, df2)
```

## I-3. Outer Join (full) 

```{r, eval=FALSE}
full_join(df1, df2)
merge(x = df1, y = df2, by = "CustomerId", all = TRUE)
```

```{r, echo=FALSE}
full_join(df1, df2)
```

## I-4. Right Join

```{r, eval=FALSE}
right_join(df1, df2)
merge(x = df1, y = df2, by = "CustomerId", all.y = TRUE)
```

```{r, echo=FALSE}
right_join(df1, df2)
```

## Summary

- Summary  

```{r, eval=FALSE}
inner_join(df1, df2)
left_join(df1, df2)
full_join(df1, df2)
right_join(df1, df2)
```

- Variations  

```{r, eval=FALSE}
inner_join(df1, df2)
inner_join(x=df1, y=df2)
inner_join(x=df1, y=df2, by = "CustomerId")
inner_join(x=df1, y=df2, by = c("CustomerId"))
inner_join(x=df1, y=df2, by = c("CustomerId"="CustomerId"))
```

## blank  



## Part II. Tidy data   

\begcols
\begcol{.48\textwidth}

```{r}
table1
```

\endcol
\begcol{.48\textwidth}

\endcol
\endcols


## II-0. Short Review (mutate)

```{r}
table1
```  
  
```{r}
table1 %>% mutate(rate = cases / popul * 100)
```  

## II-0. Short Review (group_by & summarise)

```{r}
table1
```  
  
```{r, eval=FALSE}
table1 %>% group_by(year) %>% summarise(n = sum(cases))
table1 %>% count(year, wt = cases) # equivalent to above 
```  
```{r, echo=FALSE}
table1 %>% group_by(year) %>% summarise(n = sum(cases))
```

## blank  

## II-1. `gather` from `table4a` & `table4b`

\begcols
\begcol{.48\textwidth}

```{r}
table4a
tidy4a <- table4a %>% 
  gather(colnames(table4a)[-1], 
         key = "year", 
         value = "cases")
tidy4a
```

\endcol
\begcol{.48\textwidth}

```{r}
table4b
tidy4b <- table4b %>% 
  gather(colnames(table4b)[-1], 
         key = "year", 
         value = "popul")
tidy4b
```

\endcol
\endcols

## II-1. `gather` from `table4a` & `table4b`

```{r, eval=FALSE}
left_join(tidy4a, tidy4b)
left_join(tidy4a, tidy4b, by = c("ISO3", "year"))
left_join(tidy4a, tidy4b, by = c("ISO3"="ISO3", "year"="year"))
```

```{r, echo=FALSE}
left_join(tidy4a, tidy4b)
```

## II-2. `spread` from `table2`

```{r}
table2
table2 %>% spread(key = "type", value = "count")
```

## II-3. `separate` from `table3`

```{r}
table3
table3 %>% separate(rate, into = c("cases", "popul"), sep = "/")
```

\vspace{20pt}
**Classic method**    
```{r}
table3$cases <- 
  sapply(strsplit(table3$rate, split = "/"), 
         function(x) x[1])
table3$popul <- 
  sapply(strsplit(table3$rate, split = "/"), 
         function(x) x[2])
```

## blank

## blank
