---
title: "Review - Week1"
author: "learningSpoonsR"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(results = 'hide')
```

## Module 1 - Hello World  

`r problem <- 1`   

**Problem** `r problem`. `r problem <- problem + 1` 
```{r}
a <- "Hello"
a
```
ans:  


**Problem** `r problem`. `r problem <- problem + 1` 
```{r}
a <- "Hello"
b <- "World"
paste(a,b)
```
ans:  


**Problem** `r problem`. `r problem <- problem + 1` 
```{r}
paste0(a,b)
```
ans:  


**Problem** `r problem`. `r problem <- problem + 1` 
```{r}
paste(a,b,sep="-")
```
ans:  


## Module 2 - Data Type  

`r problem <- 1`  

**Problem** `r problem`. `r problem <- problem + 1`  
```{r}
font <- "The quick brown fox"
substr(font, 4, 7)
```
ans:  


**Problem** `r problem`. `r problem <- problem + 1`  
```{r}
nchar(font)
```
ans:  


**Problem** `r problem`. `r problem <- problem + 1`  
```{r}
grep("ui", font)
```
```{r, echo=FALSE}
ans0 <- "ANS: The function grep somehow returns 0 or 1, which is equivalent to TRUE or FALSE!"
ans0
```
ans:


**Problem** `r problem`. `r problem <- problem + 1`  
```{r}
gsub("brown", "white", font)
```
ans:


**Problem** `r problem`. `r problem <- problem + 1`  
위의 명령은 다음과 같이 사용할 수도 있습니다.  어떤 장단점이 있을까요?  
```{r}
gsub(pattern = "brown", replace = "white", x=font)
```
ans:  


```{r, echo=FALSE}
ans1 <- "ANS: This is easier to understand, but a lengthy code."
ans2 <- "If frequent and obvious, go with the previous way."
paste(ans1, ans2)
```


**Problem** `r problem`. `r problem <- problem + 1`  
```{r}
aprilFool <- "2018-04-01"
class(aprilFool)
```
ans:


**Problem** `r problem`. `r problem <- problem + 1` 
```{r}
as.Date(aprilFool)
class(aprilFool)
```
```{r, echo=FALSE}
ans3 <- "ANS: Whoops! We have not assign conversion to the variable!"
ans3
```
ans:


**Problem** `r problem`. `r problem <- problem + 1` 
```{r}
bool1 <- 2==5
bool2 <- grep(pattern = "el", x = "Hello World")
paste(bool1, bool2)
```
```{r, echo=FALSE}
ans4 <- "ANS: paste(bool1, as.character(bool2)) will give \"FALSE TRUE\"."
cat(ans4)
```



